---
title: "Fantasy Hockey Analytics Week 6"
author: "Jason Winik"
date: "2/22/2021"
output: pdf_document
---

```{r setup, echo = FALSE, results = 'hide', warning = FALSE, message=FALSE}
setwd("C:/Users/jwini/OneDrive/Documents/Hockey_Stats/Fantasy Analytics/Week 6")
library(tidyverse)
fantasyteams <- read.csv("Fantasy Teams 2.21.csv")
# Total Weekly Points downloaded from NST
week6.pts <- read.csv("NST week 6.csv")
# Weekly Powerplay Points. Same data set as above filtered for PP and removing everything but PP Points.
week6.pp <- read.csv("NST week 6 PP.csv")
week6.pp.clean <- week6.pp %>%
  select(Player, Goals, Total.Assists, Total.Points) %>%
  rename(PP.Goals = Goals,
         PP.Assists = Total.Assists,
         PP.Points = Total.Points)
colnames(week6.pp.clean) <- c("Player",
                              "PP.Goals",
                              "PP.Assists",
                              "PP.Points")
# Weekly Shorthanded Points. Same data set as above filtered for PP and removing everything but PP Points.
week6.sh <- read.csv("NST week 6 SH.csv")
week6.sh.clean <- week6.sh %>%
  select(Player, Team, Goals, Total.Assists, Total.Points)
colnames(week6.sh.clean) <- c("Player",
                              "Team",
                              "SH.Goals",
                              "SH.Assists",
                              "SH.Points")
## Merge Regular Stats, PP, and SH
week6.ppsh <- merge(week6.pp.clean, week6.sh.clean, by = 'Player', all = TRUE)
week6.pts.total <- merge(week6.pts, week6.ppsh, by = 'Player', all = TRUE)
week6.pts.total[is.na(week6.pts.total)] <- 0


## Merge week 6 stats and fantasy names
week6 <- merge(week6.pts.total, fantasyteams, by = 'Player', all = TRUE)

# Weekly Player Fantasy Points
## Note this does NOT include hat tricks
week6 <- week6 %>%
  mutate(Goals.f = Goals * 4) %>%
  mutate(Assists.f = Total.Assists * 2) %>%
  mutate(PPP.f = PP.Points * 1) %>%
  mutate(SHP.f = SH.Points * 1) %>%
  mutate(SOG.f = Shots * .15) %>%
  mutate(HIT.f = Hits * .15) %>%
  mutate(BLK.f = Shots.Blocked * .2) %>%
  mutate(TOTAL.F = (Goals.f +
                         Assists.f + 
                         PPP.f + 
                         SHP.f + 
                         SOG.f +
                         HIT.f +
                         BLK.f))
week6[is.na(week6)] <- 0
```


```{r,echo=FALSE}
week6.noFA <- week6 %>%
  filter(Team != 0)
## Team Fantasy Points
week6.noFA %>%
  group_by(Team) %>%
  summarise('Fantasy Points' = sum(TOTAL.F))



#Goals vs Expected Goals

xG_week6 <- week6.noFA %>%
  group_by(Team) %>%
  summarise('Total Goals' = sum(Goals),
            'G/Skater' = mean(Goals),
            'TOTAL ixG' = sum(ixG),
            'ixG/Skater' = mean(ixG),
            'G - ixG' = sum(Goals) - sum(ixG))
xG_week6
write.csv(xG_week6, file = "xG_week6.csv")

```
Note that that these are just player stats (not including goalies) and are calculating weekly points based on if you had the same players as of Sunday night. 

# Week 6 All Teams
```{r, echo = FALSE}
##scatterplot Fantasy Points per xG
week6.noFA <- week6 %>%
  filter(Team != 0)

ggplot(week6.noFA, aes(x = TOTAL.F, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per Expected Goals",
       x = "Fantasy Points",
       y = "Expected Goals")
ggplot(week6.noFA, aes(x = TOTAL.F, y = TOI, color = Team))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per TOI",
       x = "Fantasy Points",
       y = "TOI")
ggplot(week6.noFA, aes(x = Goals, y = ixG, color = Team))+
  geom_point() +
  labs(title = "Week 6 Goals vs Expected Goals",
       x = "Goals",
       y = "Expected Goals")

```

# Individual Team Stats - TB12 West
## Trading Block Tony
```{r, echo = FALSE}
week6.noFA %>%
  filter(Owner == 'Jason Winik')%>%
  ggplot(aes(x = TOTAL.F, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per Expected Goals",
       x = "Fantasy Points",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Jason Winik', as.character(Player),'')), hjust = "inward", vjust = "inward")
week6.noFA %>%
  filter(Owner == 'Jason Winik')%>%  
ggplot(aes(x = TOTAL.F, y = TOI, color = Team))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per TOI",
       x = "Fantasy Points",
       y = "TOI") +
  geom_text(aes(label = ifelse(Owner == 'Jason Winik', as.character(Player),'')), hjust = "inward", vjust = "inward")
week6.noFA %>%
  filter(Owner == 'Jason Winik')%>%
ggplot(aes(x = Goals, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Goals vs Expected Goals",
       x = "Goals",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Jason Winik', as.character(Player),'')), hjust = "inward", vjust = "inward")

```

## That Hoser Over There
```{r, echo = FALSE}
week6.noFA %>%
  filter(Owner == 'Gaurav Shastri')%>%
  ggplot(aes(x = TOTAL.F, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per Expected Goals",
       x = "Fantasy Points",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Gaurav Shastri', as.character(Player),'')), hjust = "inward", vjust = "inward")
week6.noFA %>%
  filter(Owner == 'Gaurav Shastri')%>%
  ggplot(aes(x = TOTAL.F, y = TOI, color = Team))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per TOI",
       x = "Fantasy Points",
       y = "TOI") +
  geom_text(aes(label = ifelse(Owner == 'Gaurav Shastri', as.character(Player),'')), hjust = "inward", vjust = "inward")

week6.noFA %>%
  filter(Owner == 'Gaurav Shastri')%>%
  ggplot(aes(x = Goals, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Goals vs Expected Goals",
       x = "Goals",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Gaurav Shastri', as.character(Player),'')), hjust = "inward", vjust = "inward")

```

## Team Ginsberg
```{r, echo = FALSE}
week6.noFA %>%
  filter(Owner == 'Brandon Ginsberg')%>%
  ggplot(aes(x = TOTAL.F, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per Expected Goals",
       x = "Fantasy Points",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Brandon Ginsberg', as.character(Player),'')), hjust = "inward", vjust = "inward")
week6.noFA %>%
  filter(Owner == 'Brandon Ginsberg')%>%
  ggplot(aes(x = TOTAL.F, y = TOI, color = Team))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per TOI",
       x = "Fantasy Points",
       y = "TOI") +
  geom_text(aes(label = ifelse(Owner == 'Brandon Ginsberg', as.character(Player),'')), hjust = "inward", vjust = "inward")

week6.noFA %>%
  filter(Owner == 'Brandon Ginsberg')%>%
  ggplot(aes(x = Goals, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Goals vs Expected Goals",
       x = "Goals",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Brandon Ginsberg', as.character(Player),'')), hjust = "inward", vjust = "inward")

```

## Team Hector
```{r, echo = FALSE}
week6.noFA %>%
  filter(Owner == 'Markus Hector')%>%
  ggplot(aes(x = TOTAL.F, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per Expected Goals",
       x = "Fantasy Points",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Markus Hector', as.character(Player),'')), hjust = "inward", vjust = "inward")
week6.noFA %>%
  filter(Owner == 'Markus Hector')%>%
  ggplot(aes(x = TOTAL.F, y = TOI, color = Team))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per TOI",
       x = "Fantasy Points",
       y = "TOI") +
  geom_text(aes(label = ifelse(Owner == 'Markus Hector', as.character(Player),'')), hjust = "inward", vjust = "inward")
week6.noFA %>%
  filter(Owner == 'Markus Hector')%>%
  ggplot(aes(x = Goals, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Goals vs Expected Goals",
       x = "Goals",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Markus Hector', as.character(Player),'')), hjust = "inward", vjust = "inward")
```

## Esther Island Esthers
```{r, echo = FALSE}
week6.noFA %>%
  filter(Owner == 'Benton Croop')%>%
  ggplot(aes(x = TOTAL.F, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per Expected Goals",
       x = "Fantasy Points",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Benton Croop', as.character(Player),'')), hjust = "inward", vjust = "inward")
week6.noFA %>%
  filter(Owner == 'Benton Croop')%>%
  ggplot(aes(x = TOTAL.F, y = TOI, color = Team))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per TOI",
       x = "Fantasy Points",
       y = "TOI") +
  geom_text(aes(label = ifelse(Owner == 'Benton Croop', as.character(Player),'')), hjust = "inward", vjust = "inward")
week6.noFA %>%
  filter(Owner == 'Benton Croop')%>%
  ggplot(aes(x = Goals, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Goals vs Expected Goals",
       x = "Goals",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Benton Croop', as.character(Player),'')), hjust = "inward", vjust = "inward")

```

# Individual Team Stats - ExxonMobil East Division}
## Vasili's Pod Squad
```{r, echo = FALSE}
week6.noFA %>%
  filter(Owner == 'Will Klajbor')%>%
  ggplot(aes(x = TOTAL.F, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per Expected Goals",
       x = "Fantasy Points",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Will Klajbor', as.character(Player),'')), hjust = "inward", vjust = "inward")
week6.noFA %>%
  filter(Owner == 'Will Klajbor')%>%
  ggplot(aes(x = TOTAL.F, y = TOI, color = Team))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per TOI",
       x = "Fantasy Points",
       y = "TOI") +
  geom_text(aes(label = ifelse(Owner == 'Will Klajbor', as.character(Player),'')), hjust = "inward", vjust = "inward")
week6.noFA %>%
  filter(Owner == 'Will Klajbor')%>%
  ggplot(aes(x = Goals, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Goals vs Expected Goals",
       x = "Goals",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Will Klajbor', as.character(Player),'')), hjust = "inward", vjust = "inward")

```

## Baltimore Bandits
```{r, echo = FALSE}
week6.noFA %>%
  filter(Owner == 'Nick Arnold')%>%
  ggplot(aes(x = TOTAL.F, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per Expected Goals",
       x = "Fantasy Points",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Nick Arnold', as.character(Player),'')), hjust = "inward", vjust = "inward")
week6.noFA %>%
  filter(Owner == 'Nick Arnold')%>%
  ggplot(aes(x = TOTAL.F, y = TOI, color = Team))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per TOI",
       x = "Fantasy Points",
       y = "TOI") +
  geom_text(aes(label = ifelse(Owner == 'Nick Arnold', as.character(Player),'')), hjust = "inward", vjust = "inward")
week6.noFA %>%
  filter(Owner == 'Nick Arnold')%>%
  ggplot(aes(x = Goals, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Goals vs Expected Goals",
       x = "Goals",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Nick Arnold', as.character(Player),'')), hjust = "inward", vjust = "inward")
```

## Laussanne Automatons
```{r, echo = FALSE}
week6.noFA %>%
  filter(Owner == 'Alex Rusnak')%>%
  ggplot(aes(x = TOTAL.F, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per Expected Goals",
       x = "Fantasy Points",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Alex Rusnak', as.character(Player),'')), hjust = "inward", vjust = "inward")
week6.noFA %>%
  filter(Owner == 'Alex Rusnak')%>%
  ggplot(aes(x = TOTAL.F, y = TOI, color = Team))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per TOI",
       x = "Fantasy Points",
       y = "TOI") +
  geom_text(aes(label = ifelse(Owner == 'Alex Rusnak', as.character(Player),'')), hjust = "inward", vjust = "inward")
week6.noFA %>%
  filter(Owner == 'Alex Rusnak')%>%
  ggplot(aes(x = Goals, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Goals vs Expected Goals",
       x = "Goals",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Alex Rusnak', as.character(Player),'')), hjust = "inward", vjust = "inward")
```

## Brown Shoes w/ a Black Belt?
```{r, echo = FALSE}
week6.noFA %>%
  filter(Owner == 'Patrick Jefferson')%>%
  ggplot(aes(x = TOTAL.F, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per Expected Goals",
       x = "Fantasy Points",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Patrick Jefferson', as.character(Player),'')), hjust = "inward", vjust = "inward")
week6.noFA %>%
  filter(Owner == 'Patrick Jefferson')%>%
  ggplot(aes(x = TOTAL.F, y = TOI, color = Team))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per TOI",
       x = "Fantasy Points",
       y = "TOI") +
  geom_text(aes(label = ifelse(Owner == 'Patrick Jefferson', as.character(Player),'')), hjust = "inward", vjust = "inward")
week6.noFA %>%
  filter(Owner == 'Patrick Jefferson')%>%
  ggplot(aes(x = Goals, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Goals vs Expected Goals",
       x = "Goals",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Patrick Jefferson', as.character(Player),'')), hjust = "inward", vjust = "inward")
```

## Wayne County Firepucks
```{r, echo = FALSE}
week6.noFA %>%
  filter(Owner == 'Thomas Clark')%>%
  ggplot(aes(x = TOTAL.F, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per Expected Goals",
       x = "Fantasy Points",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Thomas Clark', as.character(Player),'')), hjust = "inward", vjust = "inward")
week6.noFA %>%
  filter(Owner == 'Thomas Clark')%>%
  ggplot(aes(x = TOTAL.F, y = TOI, color = Team))+
  geom_point() +
  labs(title = "Week 6 Fantasy Points per TOI",
       x = "Fantasy Points",
       y = "TOI") +
  geom_text(aes(label = ifelse(Owner == 'Thomas Clark', as.character(Player),'')), hjust = "inward", vjust = "inward")
week6.noFA %>%
  filter(Owner == 'Thomas Clark')%>%
  ggplot(aes(x = Goals, y = ixG, color = Team, label = Player))+
  geom_point() +
  labs(title = "Week 6 Goals vs Expected Goals",
       x = "Goals",
       y = "Expected Goals") +
  geom_text(aes(label = ifelse(Owner == 'Thomas Clark', as.character(Player),'')), hjust = "inward", vjust = "inward")
```